Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of Strategies in the Moran process for the Iterated Prisoner's Dilemma

### 2018-10-05 main.tex
Final editorial requests:
- Remove footnote;
- Remove figures;
- Fix bibliographic style.
- Re order bibliographic items.
- Remove the subfigures.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[draft, width=\textwidth]{Fig1.eps}
    \caption{A diagrammatic representation of a Moran process.}
    \label{fig:moran_process}
\end{figure}

@@

All of the training code is archived at~\cite{marc_harper_2017_824264}. This
software is (similarly to the Axelrod library) available on
GitHub\footnote{\url{https://github.com/Axelrod-Python/axelrod-dojo}}
with documentation to
train new strategies easily. Training
typically takes less than 100 generations and can be completed within several
hours on commodity hardware.

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[draft, width=\textwidth]{Fig2.eps}
    \caption{TF1: a 16 state finite state machine with a handshake leading to
    mutual cooperation at state 4.}
    \label{fig:tf1}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[draft, width=\textwidth]{Fig3.eps}
    \caption{TF2: a 16 state finite state machine with a handshake leading to
    mutual cooperation at state 16.}
    \label{fig:tf2}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[draft, width=\textwidth]{Fig4.eps}
    \caption{TF3: an 8 state finite state machine.}
    \label{fig:tf3}
\end{figure}

@@

Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
Fig~\ref{fig:comparison_deterministic} for Alternator and WSLS (a 5\%
confidence interval computed using an asymptotic normal approximation is also
included \cite{brown2001interval}).
The points represent the simulated
values and the line shows the theoretical value. Note that these are
deterministic strategies and show a good match between the expected value
of (\ref{equ:fixation_probability}) and the actual Moran process for all
strategy pairs. These means have been compared using a \(t\)-test and the \(p\)
values are shown in Table~\ref{tab:comparison_deterministic} which confirms the
fact that the theoretic and simulated values are a good match.

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[draft, width=.95\columnwidth]{./Fig5.eps}
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textit{deterministic} strategies: Alternator and
         Cooperator. 5\% confidence intervals calculated using an asymptotic
     normal approximation.
The top most line on all figures (in red and using a circle) corresponds to
\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
\(x_{1}\).}
    \label{fig:comparison_deterministic}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[draft, width=.95\columnwidth]{./Fig6.eps}
    \caption{Comparison of theoretic and actual Moran Process
             fixation probabilities for \textit{stochastic} strategies:
             Calculator and Arrogant Q Learner. 5\% confidence intervals calculated using an asymptotic
     normal approximation.
The top most line on all figures (in red and using a circle) corresponds to
\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
\(x_{1}\).}
    \label{fig:comparison_stochastic}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[draft, width=\columnwidth]{./Fig7.eps}
    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different population sizes.}
    \label{fig:ranks_v_size_invade}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[draft, width=\columnwidth]{./Fig8.eps}
    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
    population sizes.}
    \label{fig:ranks_v_size_resist}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[draft, width=\columnwidth]{./Fig9.eps}
    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
    population sizes.}
    \label{fig:ranks_v_size_coexist}
\end{figure}

@@

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[draft, width=\columnwidth]{./Fig10.eps}
        \caption{Rank based on \(x_1\)}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[draft, width=\columnwidth]{./Fig11.eps}
        \caption{Rank based on \(x_{N - 1}\)}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[draft, width=\columnwidth]{./Fig12.eps}
        \caption{Rank based on \(x_{N/2}\)}
    \end{subfigure}
    \caption{Heatmap of correlation coefficients of rankings by population size.}
    \label{fig:correlation_coefficients}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[draft, width=\columnwidth]{./Fig13.eps}
        \caption{TF1}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[draft, width=\columnwidth]{./Fig14.eps}
        \caption{TF2}
    \end{subfigure}

    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[draft, width=\columnwidth]{./Fig15.eps}
        \caption{TF3}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[draft, width=\columnwidth]{./Fig16.eps}
        \caption{CS}
    \end{subfigure}
    \caption{Cooperation rate per round (over 10000 repetitions). Rows
        correspond to all the strategies considered in this work (ordered
    alphabetically by name). Columns correspond to round of an IPD match.}
    \label{fig:cooperation_rates}
\end{figure}

@@

\bibitem{Adami2013}
Christoph Adami and Arend Hintze.
\newblock {Evolutionary instability of zero-determinant strategies demonstrates
  that winning is not everything.}
\newblock {\em Nature communications}, 4(1):2193, 2013.

\bibitem{adami2016evolutionary}
Christoph Adami, Jory Schossau, and Arend Hintze.
\newblock {Evolutionary game theory using agent-based methods}.
\newblock {\em Physics of Life Reviews}, 19(Supplement C):1 -- 26, 2016.

\bibitem{affenzeller2009genetic}
Michael Affenzeller, Stefan Wagner, Stephan Winkler, and Andreas Beham.
\newblock {\em Genetic Algorithms and Genetic Programming: Modern Concepts and
  Practical Applications}.
\newblock Numerical Insights. CRC Press, 2009.

\bibitem{Nowak2017}
Benjamin Allen, Gabor Lippner, Yu-Ting Chen, Babak Fotouhi, Naghmeh Momeni,
  Shing-Tung Yau, and Martin~A Nowak.
\newblock {Evolutionary dynamics on any population structure}.
\newblock 544:227--230, March 2017.

\bibitem{Ashlock2015}
Daniel Ashlock, Joseph~Alexander Brown, and Philip Hingston.
\newblock {Multiple Opponent Optimization of Prisoner’s Dilemma Playing
  Agents}.
\newblock {\em IEEE Transactions on Computational Intelligence and AI in
  Games}, 7(1):53--65, 2015.

\bibitem{Ashlock2008}
Daniel Ashlock and Eun-Youn Kim.
\newblock {Fingerprinting: Visualization and automatic analysis of prisoner's
  dilemma strategies}.
\newblock {\em IEEE Transactions on Evolutionary Computation}, 12(5):647--659,
  2008.

\bibitem{Ashlock2007}
Wendy Ashlock
\newblock {Why some representations are more cooperative than others for
prisoner's dilemma}
\newblock {\em Foundations of Computational Intelligence, 2007. FOCI 2007. IEEE
symposium on}, 314--321,
  2007.

\bibitem{Ashlock2006}
Wendy Ashlock and Daniel Ashlock.
\newblock {Changes in prisoner’s dilemma strategies over evolutionary time
  with different population sizes}.
\newblock In {\em Evolutionary Computation, 2006. CEC 2006. IEEE Congress on},
  pages 297--304. IEEE, 2006.

\bibitem{AshlockBook}
Daniel Ashlock.
\newblock{Evolutionary computation for modeling and optimization},
\newblock{Springer Science \& Business Media}
2006

\bibitem{Ashlock2014}
Wendy Ashlock, Jeffrey Tsang, and Daniel Ashlock.
\newblock {The evolution of exploitation}.
\newblock In {\em Foundations of Computational Intelligence (FOCI), 2014 IEEE
  Symposium on}, pages 135--142. IEEE, 2014.

\bibitem{Axelrod1980a}
Robert Axelrod.
\newblock {Effective choice in the prisoner's dilemma}.
\newblock {\em Journal of conflict resolution}, 24(1):3--25, 1980.

\bibitem{Axelrod1980b}
Robert Axelrod.
\newblock {More Effective Choice in the Prisoner's Dilemma}.
\newblock {\em Journal of Conflict Resolution}, 24(3):379--403, 1980.

\bibitem{Axelrod1984}
Robert Axelrod.
\newblock {\em The Evolution of Cooperation}.
\newblock Basic books. Basic Books, 1984.

\bibitem{Baek2016}
{Baek, Seung Ki and Jeong, Hyeong-chai and Hilbe, Christian and Nowak, Martin
  A}.
\newblock {Comparing reactive and memory- one strategies of direct
  reciprocity}.
\newblock {\em Nature Publishing Group}, pages 1--13, 2016.

\bibitem{Banks1990}
Jeffrey~S Banks and Rangarajan~K Sundaram.
\newblock {Repeated games, finite automata, and complexity}.
\newblock {\em Games and Economic Behavior}, 2(2):97--117, 1990.

\bibitem{Beaufils1997}
Bruno Beaufils, Jean-Paul Delahaye, and Philippe Mathieu.
\newblock {Our meeting with gradual, a good strategy for the iterated
  prisoner’s dilemma}.
\newblock In {\em Proceedings of the Fifth International Workshop on the
  Synthesis and Simulation of Living Systems}, pages 202--209, 1997.

\bibitem{brown2001interval}
Lawrence~D Brown, T~Tony Cai, and Anirban DasGupta.
\newblock Interval estimation for a binomial proportion.
\newblock {\em Statistical science}, pages 101--117, 2001.

\bibitem{Andre2013}
Andre~LC Carvalho, Honovan~P Rocha, Felipe~T Amaral, and Frederico~G Guimaraes.
\newblock {Iterated Prisoner’s Dilemma-An extended analysis}.
\newblock pages 1--6, 2013.

\bibitem{Eckhart2015}
Arnold Eckhart.
\newblock Coopsim v0.9.9 beta 6.
\newblock https://github.com/jecki/CoopSim/, 2015.

\bibitem{Flood1958}
Merrill~M Flood.
\newblock {Some Experimental Games}, 1958.

\bibitem{Frean1994}
Marcus~R Frean.
\newblock {The prisoner's dilemma without synchrony}.
\newblock {\em Proceedings of the Royal Society of London B: Biological
  Sciences}, 257(1348):75--79, 1994.

\bibitem{Gaudesi2016}
Marco Gaudesi, Elio Piccolo, Giovanni Squillero, and Alberto Tonda.
\newblock {Exploiting evolutionary modeling to prevail in iterated prisoner’s
  dilemma tournaments}.
\newblock {\em IEEE Transactions on Computational Intelligence and AI in
  Games}, 8(3):288--300, 2016.

\bibitem{marc_harper_2017_824264}
Marc Harper, Vince Knight, and Martin Jones.
\newblock Axelrod-python/axelrod-dojo: v0.0.1.
\newblock https://doi.org/10.5281/zenodo.824264, July 2017.

\bibitem{Harper2017}
Marc Harper, Vincent Knight, Martin Jones, Georgios Koutsovoulos, Nikoleta~E
  Glynatsi, and Owen Campbell.
\newblock {Reinforcement Learning Produces Dominant Strategies for the Iterated
  Prisoner's Dilemma}.
\newblock {\em PLOS ONE}, 12(12): 12 2017.

\bibitem{Hilbe2017}
Christian Hilbe, Luis~A Martinez-Vaquero, Krishnendu Chatterjee, and Martin~A
  Nowak.
\newblock {Memory-n strategies of direct reciprocity}.
\newblock {\em Proceedings of the National Academy of Sciences}, page
  201621239, 2017.

\bibitem{Hilbe2013}
Christian Hilbe, Martin~A Nowak, and Arne Traulsen.
\newblock {Adaptive dynamics of extortion and compliance}.
\newblock {\em PloS one}, 8(11):e77886, 2013.

\bibitem{hunter2007matplotlib}
John~D Hunter.
\newblock {Matplotlib: A 2D graphics environment}.
\newblock {\em Computing In Science \& Engineering}, 9(3):90--95, 2007.

\bibitem{kendall2007iterated}
Graham Kendall, Xin Yao, and Siang~Y Chong.
\newblock {\em The Iterated Prisoners' Dilemma: 20 Years on}.
\newblock Advances in natural computation. World Scientific, 2007.

\bibitem{Knight2016}
Vincent Knight, Owen Campbell, Marc Harper, Karol~M Langner, James Campbell,
  Thomas Campbell, Alex Carney, Martin Chorley, Cameron Davidson-pilon,
  Nikoleta Glynatsi, Tom{\'{a}}{\v{s}} Ehrlich, Martin Jones, Georgios
  Koutsovoulos, Jochen Muller, Geraint Palmer, Piotr Petunov, Paul Slavin,
  Timothy Standen, Luis Visintini, and Karl Molden.
\newblock {An Open Framework for the Reproducible Study of the Iterated
  Prisoner ' s Dilemma}.
\newblock 2016.

\bibitem{data}
Vincent Knight, Marc Harper, and Nikoleta~E Glynatsi.
\newblock {Data for: Evolution Reinforces Cooperation with the Emergence of
  Self-Recognition Mechanisms: an empirical study of the Moran process for the
  iterated Prisoner's dilemma using reinforcement learning}.
\newblock https://doi.org/10.5281/zenodo.1040129, July 2017.

\bibitem{Kraines1989}
David Kraines and Vivian Kraines.
\newblock {Pavlov and the prisoner's dilemma}.
\newblock {\em Theory and decision}, 26(1):47--79, 1989.

\bibitem{Kuhn2017}
Steven Kuhn.
\newblock Prisoner's dilemma.
\newblock In Edward~N. Zalta, editor, {\em The Stanford Encyclopedia of
  Philosophy}. Metaphysics Research Lab, Stanford University, spring 2017
  edition, 2017.

\bibitem{Lee2015}
Christopher Lee, Marc Harper, and Dashiell Fryer.
\newblock {The Art of War: Beyond Memory-one Strategies in Population Games}.
\newblock {\em Plos One}, 10(3):e0120625, 2015.

\bibitem{Li2011}
Jiawei Li, Philip Hingston, and Graham Kendall.
\newblock {Engineering Design of Strategies for Winning Iterated Prisoner's
  Dilemma Competitions}.
\newblock {\em IEEE Transactions on Computational Intelligence and AI in
  Games}, 3(4):348--360, 2011.

\bibitem{Li2009}
Jiawei Li and Graham Kendall.
\newblock {A strategy with novel evolutionary features for the iterated
  prisoner's dilemma.}
\newblock {\em Evolutionary Computation}, 17(2):257--274, 2009.

\bibitem{Li2014}
Jiawei Li and Graham Kendall.
\newblock {The effect of memory size on the evolutionary stability of
  strategies in iterated prisoner's dilemma}.
\newblock {\em IEEE Transactions on Evolutionary Computation}, 18(6):819--826,
  2014.

@@

\bibitem{Mateo2003}
Jill M. Mateo.
\newblock {Kin recognition in ground squirrels and other rodents}.
\newblock In {\em Journal of Mammalogy}, 84 (4), 1163--1181

\bibitem{Mathieu2015}
Philippe Mathieu and Jean-Paul Delahaye.
\newblock {New Winning Strategies for the Iterated Prisoner's Dilemma (Extended
  Abstract)}.
\newblock {\em 14th International Conference on Autonomous Agents and
  Multiagent Systems (AAMAS 2015)}, pages 1665--1666, 2015.

\bibitem{mckinney2010data}
Wes McKinney et~al.
\newblock Data structures for statistical computing in python.
\newblock In {\em Proceedings of the 9th Python in Science Conference}, volume
  445, pages 51--56. van der Voort S, Millman J, 2010.

\bibitem{Mittal2009}
Shashi Mittal and Kalyanmoy Deb.
\newblock {Optimal strategies of the iterated prisoner's dilemma problem for
  multiple conflicting objectives}.
\newblock {\em IEEE Transactions on Evolutionary Computation}, 13(3):554--565,
  2009.

\bibitem{Moran1957}
Patrick A~P Moran.
\newblock {Random Processes in Genetics}.
\newblock {\em Mathematical Proceedings of the Cambridge Philosophical
  Society}, 54(1):60--71, 1957.

\bibitem{Nachbar1992}
John~H Nachbar.
\newblock {Evolution in the finitely repeated prisoner's dilemma}.
\newblock {\em Journal of Economic Behavior \& Organization}, 19(3):307--326,
  1992.

\bibitem{Nowak}
Martin~A Nowak.
\newblock {\em Evolutionary Dynamics: Exploring the Equations of Life}.
\newblock Cambridge: Harvard University Press.

\bibitem{Nowak1993}
Martin~A Nowak and Karl Sigmund.
\newblock {A strategy of win-stay, lose-shift that outperforms tit-for-tat in
  the Prisoner's Dilemma game.}
\newblock {\em Nature}, 364(6432):56--58, 1993.

\bibitem{Press2012}
William~H Press and Freeman~J Dyson.
\newblock {Iterated Prisoner's Dilemma contains strategies that dominate any
  evolutionary opponent.}
\newblock {\em Proceedings of the National Academy of Sciences of the United
  States of America}, 109(26):10409--13, 2012.

\bibitem{Prlic2012}
Andreas Prlić and James~B Procter.
\newblock {Ten Simple Rules for the Open Development of Scientific Software}.
\newblock {\em PLOS Computational Biology}, 8(12):1--3, 12 2012.

\bibitem{Robson1990}
Arthur~J Robson.
\newblock {Efficiency in evolutionary games: Darwin, Nash and the secret
  handshake}.
\newblock {\em Journal of theoretical Biology}, 144(3):379--396, 1990.

\bibitem{Sandve2013}
Geir~Kjetil Sandve, Anton Nekrutenko, James Taylor, and Eivind Hovig.
\newblock {Ten Simple Rules for Reproducible Computational Research}.
\newblock {\em PLoS Computational Biology}, 9(10):1--4, 2013.

\bibitem{Stewart2012}
Alexander~J Stewart and Joshua~B Plotkin.
\newblock {Extortion and cooperation in the Prisoner’s Dilemma}.
\newblock {\em Proceedings of the National Academy of Sciences},
  109(26):10134--10135, 2012.

\bibitem{stewart2013extortion}
Alexander~J Stewart and Joshua~B Plotkin.
\newblock {From extortion to generosity, evolution in the iterated prisoner’s
  dilemma}.
\newblock {\em Proceedings of the National Academy of Sciences},
  110(38):15348--15353, 2013.

\bibitem{Tzafestas2000}
Elpida Tzafestas.
\newblock {Toward adaptive cooperative behavior}.
\newblock {\em From Animals to animals: Proceedings of the 6th International
  Conference on the Simulation of Adaptive Behavior {(SAB-2000)}}, 2:334--340,
  2000.

>>>>

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[ width=\textwidth]{Fig1.eps}
    \caption{A diagrammatic representation of a Moran process.}
    \label{fig:moran_process}
\end{figure}

@@

All of the training code is archived at~\cite{marc_harper_2017_824264}. This
software is (similarly to the Axelrod library) available on
GitHub~(\url{https://github.com/Axelrod-Python/axelrod-dojo})
with documentation to
train new strategies easily. Training
typically takes less than 100 generations and can be completed within several
hours on commodity hardware.

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[ width=\textwidth]{Fig2.eps}
    \caption{TF1: a 16 state finite state machine with a handshake leading to
    mutual cooperation at state 4.}
    \label{fig:tf1}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[ width=\textwidth]{Fig3.eps}
    \caption{TF2: a 16 state finite state machine with a handshake leading to
    mutual cooperation at state 16.}
    \label{fig:tf2}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[ width=\textwidth]{Fig4.eps}
    \caption{TF3: an 8 state finite state machine.}
    \label{fig:tf3}
\end{figure}

@@

Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
Fig~\ref{fig:comparison_deterministic} for Alternator and WSLS (a 5\%
confidence interval computed using an asymptotic normal approximation is also
included~\cite{brown2001interval}).
The points represent the simulated
values and the line shows the theoretical value. Note that these are
deterministic strategies and show a good match between the expected value
of (\ref{equ:fixation_probability}) and the actual Moran process for all
strategy pairs. These means have been compared using a \(t\)-test and the \(p\)
values are shown in Table~\ref{tab:comparison_deterministic} which confirms the
fact that the theoretic and simulated values are a good match.

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[ width=.95\columnwidth]{./Fig5.eps}
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textit{deterministic} strategies: Alternator and
         Cooperator. 5\% confidence intervals calculated using an asymptotic
     normal approximation.
The top most line on all figures (in red and using a circle) corresponds to
\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
\(x_{1}\).}
    \label{fig:comparison_deterministic}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[ width=.95\columnwidth]{./Fig6.eps}
    \caption{Comparison of theoretic and actual Moran Process
             fixation probabilities for \textit{stochastic} strategies:
             Calculator and Arrogant Q Learner. 5\% confidence intervals calculated using an asymptotic
     normal approximation.
The top most line on all figures (in red and using a circle) corresponds to
\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
\(x_{1}\).}
    \label{fig:comparison_stochastic}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[ width=\columnwidth]{./Fig7.eps}
    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different population sizes.}
    \label{fig:ranks_v_size_invade}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[ width=\columnwidth]{./Fig8.eps}
    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
    population sizes.}
    \label{fig:ranks_v_size_resist}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[ width=\columnwidth]{./Fig9.eps}
    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
    population sizes.}
    \label{fig:ranks_v_size_coexist}
\end{figure}

@@

\begin{figure}[!htbp]
    \centering
    %\includegraphics[ width=\columnwidth]{./Fig10.eps}
    \caption{Heatmap of correlation coefficients of rankings by population size.}
    \label{fig:correlation_coefficients}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[ width=\columnwidth]{./Fig11.eps}
    \caption{Cooperation rate per round (over 10000 repetitions). Rows
        correspond to all the strategies considered in this work (ordered
    alphabetically by name). Columns correspond to round of an IPD match.}
    \label{fig:cooperation_rates}
\end{figure}

@@

\bibitem{Flood1958}
Flood M.
\newblock {Some Experimental Games}, 1958.

\bibitem{Axelrod1980a}
Axelrod R.
\newblock {Effective choice in the prisoner's dilemma}.
\newblock {\em Journal of conflict resolution}, 24(1):3--25, 1980.

\bibitem{Knight2016}
Knight V, Campbell O, Harper M, Langner K, Campbell J,
  Campbell T, Carney A, Chorley M, Davidson-pilon C,
  Glynatsi N, Ehrlich T, Jones M, Koutsovoulos G, Muller J, Palmer G, Petunov P, Slavin P,
  Standen T, Visintini L, and Molden K.
\newblock {An Open Framework for the Reproducible Study of the Iterated
  Prisoner ' s Dilemma}.
\newblock 2016.

\bibitem{Press2012}
Press W and Dyson F.
\newblock {Iterated Prisoner's Dilemma contains strategies that dominate any
  evolutionary opponent.}
\newblock {\em Proceedings of the National Academy of Sciences of the United
  States of America}, 109(26):10409--13, 2012.

\bibitem{Moran1957}
Moran P.
\newblock {Random Processes in Genetics}.
\newblock {\em Mathematical Proceedings of the Cambridge Philosophical
  Society}, 54(1):60--71, 1957.

\bibitem{Nowak}
Nowak M.
\newblock {\em Evolutionary Dynamics: Exploring the Equations of Life}.
\newblock Cambridge: Harvard University Press.

\bibitem{stewart2013extortion}
Stewart A and Plotkin J.
\newblock {From extortion to generosity, evolution in the iterated prisoner’s
  dilemma}.
\newblock {\em Proceedings of the National Academy of Sciences},
  110(38):15348--15353, 2013.

\bibitem{adami2016evolutionary}
Adami C, Schossau J, and Hintze A.
\newblock {Evolutionary game theory using agent-based methods}.
\newblock {\em Physics of Life Reviews}, 19(Supplement C):1 -- 26, 2016.

\bibitem{Robson1990}
Robson A.
\newblock {Efficiency in evolutionary games: Darwin, Nash and the secret
  handshake}.
\newblock {\em Journal of theoretical Biology}, 144(3):379--396, 1990.

\bibitem{Mateo2003}
Mateo J.
\newblock {Kin recognition in ground squirrels and other rodents}.
\newblock In {\em Journal of Mammalogy}, 84 (4), 1163--1181

\bibitem{West2016}
West J, Hasnain Z, Mason J, and Newton P.
\newblock {The prisoner’s dilemma as a cancer model}.
\newblock {\em Convergent Science Physical Oncology}, 2(3):035002, 2016.

\bibitem{Nowak2017}
Allen B, Lippner G, Chen Y, Fotouhi B, Momeni N,
  Shing-Tung Yau, and Martin~A Nowak.
\newblock {Evolutionary dynamics on any population structure}.
\newblock 544:227--230, March 2017.

\bibitem{Li2014}
Li J and Kendall G.
\newblock {The effect of memory size on the evolutionary stability of
  strategies in iterated prisoner's dilemma}.
\newblock {\em IEEE Transactions on Evolutionary Computation}, 18(6):819--826,
  2014.

\bibitem{Baek2016}
{Seung Ki B, Hyeong-chai J, Christian H and Martin N}.
\newblock {Comparing reactive and memory- one strategies of direct
  reciprocity}.
\newblock {\em Nature Publishing Group}, pages 1--13, 2016.

\bibitem{Lee2015}
Lee C, Harper M, and Fryer D.
\newblock {The Art of War: Beyond Memory-one Strategies in Population Games}.
\newblock {\em Plos One}, 10(3):e0120625, 2015.

\bibitem{Hilbe2017}
Hilbe C, Martinez-Vaquero L, Chatterjee K, and Nowak M.
\newblock {Memory-n strategies of direct reciprocity}.
\newblock {\em Proceedings of the National Academy of Sciences}, page
  201621239, 2017.

\bibitem{Adami2013}
Adami C and Hintze A.
\newblock {Evolutionary instability of zero-determinant strategies demonstrates
  that winning is not everything.}
\newblock {\em Nature communications}, 4(1):2193, 2013.

\bibitem{Harper2017}
Harper M, Knight V, Jones M, Koutsovoulos G, Glynatsi N , and Campbell O.
\newblock {Reinforcement Learning Produces Dominant Strategies for the Iterated
  Prisoner's Dilemma}.
\newblock {\em PLOS ONE}, 12(12): 12 2017.

\bibitem{affenzeller2009genetic}
Affenzeller M, Wagner S, Winkler S, and Beham A.
\newblock {\em Genetic Algorithms and Genetic Programming: Modern Concepts and
  Practical Applications}.
\newblock Numerical Insights. CRC Press, 2009.

\bibitem{Ashlock2006}
Ashlock W and Ashlock D.
\newblock {Changes in prisoner’s dilemma strategies over evolutionary time
  with different population sizes}.
\newblock In {\em Evolutionary Computation, 2006. CEC 2006. IEEE Congress on},
  pages 297--304. IEEE, 2006.

\bibitem{Gaudesi2016}
Gaudesi M, Piccolo E, Squillero G, and Tonda A.
\newblock {Exploiting evolutionary modeling to prevail in iterated prisoner’s
  dilemma tournaments}.
\newblock {\em IEEE Transactions on Computational Intelligence and AI in
  Games}, 8(3):288--300, 2016.

\bibitem{marc_harper_2017_824264}
Harper M, Knight V, and Jones M.
\newblock Axelrod-python/axelrod-dojo: v0.0.1.
\newblock https://doi.org/10.5281/zenodo.824264, July 2017.

\bibitem{AshlockBook}
Ashlock D.
\newblock{Evolutionary computation for modeling and optimization},
\newblock{Springer Science \& Business Media}
2006

\bibitem{Ashlock2007}
Ashlock W
\newblock {Why some representations are more cooperative than others for
prisoner's dilemma}
\newblock {\em Foundations of Computational Intelligence, 2007. FOCI 2007. IEEE
symposium on}, 314--321,
  2007.

\bibitem{data}
Knight V, Harper M, and Glynatsi N.
\newblock {Data for: Evolution Reinforces Cooperation with the Emergence of
  Self-Recognition Mechanisms: an empirical study of the Moran process for the
  iterated Prisoner's dilemma using reinforcement learning}.
\newblock https://doi.org/10.5281/zenodo.1040129, July 2017.

@@

\bibitem{Li2009}
Li J and Kendall G.
\newblock {A strategy with novel evolutionary features for the iterated
  prisoner's dilemma.}
\newblock {\em Evolutionary Computation}, 17(2):257--274, 2009.

\bibitem{brown2001interval}
Brown L, Cai T, and DasGupta A.
\newblock Interval estimation for a binomial proportion.
\newblock {\em Statistical science}, pages 101--117, 2001.

\bibitem{Prlic2012}
Prlić A and Procter J.
\newblock {Ten Simple Rules for the Open Development of Scientific Software}.
\newblock {\em PLOS Computational Biology}, 8(12):1--3, 12 2012.

\bibitem{Sandve2013}
Sandve G, Nekrutenko A, Taylor J, and Hovig E.
\newblock {Ten Simple Rules for Reproducible Computational Research}.
\newblock {\em PLoS Computational Biology}, 9(10):1--4, 2013.

\bibitem{Wilson2014}
Wilson G , Aruliah D, Brown T, Chue~Hong N, Davis M ,
  Guy R , Haddock S , Huff K, Mitchell I , Plumbley M , 
  Waugh B , White E , and Wilson P.
\newblock {Best Practices for Scientific Computing}.
\newblock {\em PLOS Biology}, 12(1):1--7, 01 2014.

\bibitem{hunter2007matplotlib}
Hunter J.
\newblock {Matplotlib: A 2D graphics environment}.
\newblock {\em Computing In Science \& Engineering}, 9(3):90--95, 2007.

\bibitem{mckinney2010data}
McKinney W et~al.
\newblock Data structures for statistical computing in python.
\newblock In {\em Proceedings of the 9th Python in Science Conference}, volume
  445, pages 51--56. van der Voort S, Millman J, 2010.

\bibitem{walt2011numpy}
van~der Walt S, Colbert C, and Varoquaux G.
\newblock {The NumPy array: a structure for efficient numerical computation}.
\newblock {\em Computing in Science \& Engineering}, 13(2):22--30, 2011.

\bibitem{Li2011}
Li J, Hingston P, and Kendall G.
\newblock {Engineering Design of Strategies for Winning Iterated Prisoner's
  Dilemma Competitions}.
\newblock {\em IEEE Transactions on Computational Intelligence and AI in
  Games}, 3(4):348--360, 2011.

\bibitem{kendall2007iterated}
Kendall G, Yao X, and Chong S.
\newblock {\em The Iterated Prisoners' Dilemma: 20 Years on}.
\newblock Advances in natural computation. World Scientific, 2007.

\bibitem{Tzafestas2000}
Tzafestas E.
\newblock {Toward adaptive cooperative behavior}.
\newblock {\em From Animals to animals: Proceedings of the 6th International
  Conference on the Simulation of Adaptive Behavior {(SAB-2000)}}, 2:334--340,
  2000.

\bibitem{Axelrod1984}
Axelrod R.
\newblock {\em The Evolution of Cooperation}.
\newblock Basic books. Basic Books, 1984.

\bibitem{Mittal2009}
Mittal S and Deb K.
\newblock {Optimal strategies of the iterated prisoner's dilemma problem for
  multiple conflicting objectives}.
\newblock {\em IEEE Transactions on Evolutionary Computation}, 13(3):554--565,
  2009.

\bibitem{Hilbe2013}
Hilbe C, Nowak M, and Traulsen A.
\newblock {Adaptive dynamics of extortion and compliance}.
\newblock {\em PloS one}, 8(11):e77886, 2013.

\bibitem{Nachbar1992}
Nachbar J.
\newblock {Evolution in the finitely repeated prisoner's dilemma}.
\newblock {\em Journal of Economic Behavior \& Organization}, 19(3):307--326,
  1992.

\bibitem{Axelrod1995}
Wu J and Axelrod R .
\newblock {How to cope with noise in the iterated prisoner's dilemma}.
\newblock {\em Journal of Conflict resolution}, 39(1):183--189, 1995.

\bibitem{Berg2015}
Van~den Berg P and Weissing F.
\newblock {The importance of mechanisms for the evolution of cooperation}.
\newblock In {\em Proc. R. Soc. B}, volume 282, page 20151382. The Royal
  Society, 2015.

\bibitem{Axelrod1980b}
Axelrod R.
\newblock {More Effective Choice in the Prisoner's Dilemma}.
\newblock {\em Journal of Conflict Resolution}, 24(3):379--403, 1980.

\bibitem{Frean1994}
Frean M.
\newblock {The prisoner's dilemma without synchrony}.
\newblock {\em Proceedings of the Royal Society of London B: Biological
  Sciences}, 257(1348):75--79, 1994.

\bibitem{Nowak1993}
Nowak M and Sigmund K.
\newblock {A strategy of win-stay, lose-shift that outperforms tit-for-tat in
  the Prisoner's Dilemma game.}
\newblock {\em Nature}, 364(6432):56--58, 1993.

\bibitem{Beaufils1997}
Beaufils B, Delahaye J, and Mathieu P.
\newblock {Our meeting with gradual, a good strategy for the iterated
  prisoner’s dilemma}.
\newblock In {\em Proceedings of the Fifth International Workshop on the
  Synthesis and Simulation of Living Systems}, pages 202--209, 1997.

\bibitem{Banks1990}
Banks J and Sundaram R.
\newblock {Repeated games, finite automata, and complexity}.
\newblock {\em Games and Economic Behavior}, 2(2):97--117, 1990.
